% \subsection{Online journal article}
% \tbhead
% \mtr{Journal article accessed via a library database}&
% 	Boon (2011) examines...&
% 		\textcite{Boon2011} examines...&
% 		\mtr{Boon, KA 2011, ‘Ethics and capitalism in the screenplays of David Mamet’, \textit{Literature Film Quarterly}, vol. 39, no. 3, pp. 174–89.}&
% 		\mtr{\fullcite{Boon2011}}&
% 		\mtri{When an article is accessed using an electronic database, reference it as a standard journal article (see Print section): do not include date viewed, URL, or refer to the database.}
% 		\tabularnewline
% &
% 	...potent subtext (Boon 2011, p. 181).&
% 		...potent subtext \parencite{Boon2011}.
% 		\tabularnewline
% \bottomrule\end{longtabu}
\subsection{Online journal article}
\tbhead
\mtr{Journal article accessed via a library database}&
	Boon (2011) examines...&
		\textcite{Boon2011} examines...&
		\mtr{Boon, KA 2011, ‘Ethics and capitalism in the screenplays of David Mamet’, \textit{Literature Film Quarterly}, vol. 39, no. 3, pp. 174–89.}&
		\mtr{\fullcite{Boon2011}}&
		\mtri{When an article is accessed using an electronic database, reference it as a standard journal article (see Print section): do not include date viewed, URL, or refer to the database.}
		\tabularnewline
&
	...potent subtext (Boon 2011, p. 181).&
		...potent subtext \parencite[181]{Boon2011}.&
		\tabularnewline
\mtr{PDF version of a print journal article accessed via the internet (e.g. Google, Google Scholar, Muse, JSTOR)}&
	Werstine (1999, p. 311) laments...&
		\textcite[311]{Werstine1999} laments...&
		\mtr{Werstine, P 1999, ‘A century of “bad” Shakespeare quartos’, Shakespeare Quarterly, vol. 50, no. 3, pp. 310–33.}&
		\mtr{\fullcite{Werstine1999}}&
		\mtri{When the article is a scanned PDF version of a print journal article that you found online, reference it as a standard journal article (see Print section). If unsure about its print or online origin, include date viewed and URL.}
		\tabularnewline
&		
	..inherently flawed (Werstine 1999, p. 311).&
		..inherently flawed \parencite[311]{Werstine1999}.
		\tabularnewline
Journal article from an electronic journal’s own website&
	Blamires (2012) writes...&
		\textcite{Blamires2012} writes...&
		Blamires, A 2012, ‘Homoerotic pleasure and violence in the drama of Thomas Middleton’, \textit{Early Modern Literary Studies}, vol. 16, no. 2, viewed 11 November 2012, <\url{http://extra.shu.ac.uk/emls/16- 2/blammidd.htm}>.&
		\fullcite{Blamires2012}&
		\mtr{When an article is accessed directly from the e-journal’s own website, include date viewed and URL. Note that conventions for volume, issue, and pagination may vary between online journals.}
		\tabularnewline
&
	...in nursing (Murray 2012, p. 57).&
		...in nursing \parencite[57]{Murray2012}.&
		Murray, N 2012, ‘A report on a pilot English language intervention model for undergraduate trainee nurses’, \textit{Journal of Academic Language and Learning}, vol. 6, no. 1, pp. 48–63, viewed 7 May 2016, <\url{http://journal.aall.org.au/index.php/jall/article/view/135/128}>.&
		\fullcite{Murray2012}
		\tabularnewline
\bottomrule\end{longtabu}