\section{Other}
\tbhead{}
\mtr{Computer programs and software (including apps)}
	... program was developed (MathWorks 2010).&
		... program was developed \parencite{matlab}.&
		MathWorks 2010, \textit{MATLAB}, ver. 7.11, computer program, The MathWorks Inc., Natick, Mass.&
		\fullcite{matlab}
		\tabularnewline
&
	... the ABC iview app (Australian Broadcasting Corporation 2016).
		... the \citetitle{ABCiViewApp} app \parencite{ABCiViewApp}.
		Australian Broadcasting Corporation 2016, \textit{ABC iview}, version 3.12, mobile application, Australian Broadcasting Corporation, viewed 4 October 2016, <\url{https://itunes.apple.com/au/app/abc-iview/id401778175?mt=8}/>.
		\tabularnewline
Artwork (e.g. painting, sculpture)&
	Piccinini’s 2005 sculpture \textit{Big Mother}, housed in the Art Gallery of South Australia, presents...&
		Piccinini’s 2005 sculpture \citetitle{}, housed in the Art Gallery of South Australia, presents...&
		&
		\fullcite{}&
		\mtri{Works of art and live performances cannot be easily recovered by readers, so describe them in detail in- text instead of referencing.}
		\tabularnewline
Live performance (e.g. theatre, speech)&
	The State Theatre Company of South Australia’s 2012 production of \textit{In the next room; or the vibrator play} drew...&
		\tabularnewline
Personal communication (e.g. letters, conversation)&
	... as reported in private correspondence on 31 October...&
		... as reported in private correspondence on \citedate{}...&
		&&
		\instruction{Do not create references for correspondence or conversations: describe in-text.}
		\tabularnewline
Image/\linebreak[1]diagram/\linebreak[1]artwork from a print source&
	Modes of support (Hussin 2007, p. 365).&
		Modes of support \parencite[365]{Hussin2007}.&
		Hussin, V 2007, ‘Supporting off-shore students: a preliminary study’, \textit{Innovations in Education Teaching International}, vol. 44, no. 4, pp. 363–76.&
		\fullcite{Hussin2007}&
		\mtri{Cite the source where the image was located using the standard format for that source.}
		\tabularnewline
Image/\linebreak[1]diagram/\linebreak[1]artwork from an online source&
	Neil Armstrong (NASA 2008).&
		Neil Armstrong \parencite{}.&
		NASA 2008, \textit{Image of the day gallery: a man on the moon}, NASA, 23 March, viewed 27 November 2012, <\url{http://www.nasa.gov/multimedia/imagegallery/image_feature_369a.html}>.&
		\fullcite{}
		\tabularnewline
Image/\linebreak[1]diagram/\linebreak[1]artwork (your own)&
	The Rectangle (Author’s own 2017, unpublished).&
		The Rectangle (Author’s own 2017, unpublished).&
		&&
		\instruction{Not listed in reference list as cannot be recovered by reader.}
		\tabularnewline
Map&
	According to the map of the region (Department of Employment, Economic Development and Innovations Queensland 2010) there are...&
		According to the map of the region \parencite{} there are...&
		Department of Employment, Economic Development and Innovations Queensland 2010, \textit{Queensland’s mineral, petroleum and energy operations and resources}, Department of Mines and Energy Queensland, Brisbane.&
		\instruction{If the map is derived from an Atlas, cite the Atlas in standard book format.}
		\tabularnewline
\bottomrule\end{longtabu}