\subsubsection{Edited Book}
\tbhead
	\mtr{Edited (ed.) or compiled (comp.) book}&
		Hornberger (ed. 2003) questions whether...&
			\textcite{Hornberger2003} questions whether...&
			Hornberger, NH (ed.) 2003, \textit{Continua of biliteracy: an ecological framework for educational policy, research and practice in multilingual settings}, Multilingual Matters, Clevedon, UK.&
			\fullcite{Hornberger2003}&
			\mtr{%
				\instruction{When the editor’s name is included within your sentence (not in brackets) place ed. in the brackets following their name. When the editor’s name is in brackets, put ed. before their name.}
				\ls
				\todow{neither textcite nor parencite produce the ed. note}
				\ls
				\todow{Support compiler instead of editor tag}
				}
			\tabularnewline
\badrow{8}		&It is not clear whether this point supports his previous assertions (ed. Hornberger 2003).&
			It is not clear whether this point supports his previous assertions \parencite{Hornberger2003}
			\tabularnewline
	\midrule
	Edited (ed.) or compiled (comp.) book with 2 or 3 editors&
		Kronenberg, Pollard and Sakellariou (eds 2011) are interested in providing a framework for...&
			\textcite{Kronenberg2011} are interested in providing a framework for...&
			\mtr{Kronenberg, F, Pollard, N \& Sakellariou, D (eds) 2011, \textit{Occupational therapies without borders: towards an ecology of occupation-based practices}, vol. 2, Churchill Livingstone Elsevier, Edinburgh.}&
			\mtr{\fullcite{Kronenberg2011}}&
			\mtri{When editors’ names are included within your sentence (not in brackets) use the full spelling of ‘and’. When their names are in brackets or in the reference list, use ‘\&’.\ls Note the use of ‘eds’ (no full stop) for multiple editors.}
			\tabularnewline
		&...is included in this framework (eds Kronenberg, Pollard \& Sakellariou 2011).	&...is included in this framework \parencite{Kronenberg2011}.&
			\tabularnewline
Edited book with 4 or more editors&
	In their collection of essays, Barnett et al. (eds 2006) explore...&
		In their collection of essays, \textcite{Barnett2006} explore...&
		Barnett, T, Bierbaum, N, Harrex, S, Hosking, R \& Tulloch, G (eds) 2006, \textit{London was full of rooms}, Lythrum Press, Adelaide.&
		\fullcite{Barnett2006}&
		\instruction{When there are 4 or more editors, only use the first editor’s name in-text followed by the abbreviation et al. But include all names in the reference list.}
		\tabularnewline
% \bottomrule\end{longtabu}
% \subsubsection{Chapter in an edited book}
% \tbhead
\midrule
	Chapter in an edited book&
		Abbott (2010, p. 32) believes the horror blockbuster...&
			\textcite[32]{Abbott2010} believes the horror blockbuster...&
			Abbott, S 2010, `High concept thrills and chills: the horror blockbuster’, in I Conrich (ed.), \textit{Horror zone: the cultural experience of contemporary horror cinema}, I.B. Tauris, London, pp. 27–44.&
			\fullcite{Abbott2010}&
			\mtri{Use the chapter author in your in-text reference. In the reference list the editor comes after the chapter title and is preceded by ‘in’. Note the exception to the order of initials for editors– for chapters put the editor’s initial(s) before family name.}
			\tabularnewline
	&
		...influential theory (Naremore 2004, p. 11).&
			...influential theory \parencite[11]{Naremore2004}.&
			Naremore, J 2004, `Authorship’, in T Miller \& R Stam (eds), \textit{A companion to film theory}, Blackwell Publishing, Malden, Massachusetts, pp. 9–24.&
			\fullcite{Naremore2004}
			\tabularnewline
\bottomrule\end{longtabu}