\subsection{Articles}
\subsubsection{Journal Article}
\tbhead
Journal article&
	O’Hara (2009, p. 1548) supports...&
		\textcite[1548]{OHara2009} supports...&
		O’Hara, MJ 2009, `Flood basalts, basalt floods or topless bushvelds? Lunar petrogenesis revisited’, \textit{Journal of Petrology}, vol. 41, no. 11, pp. 1545–1651.&
		\fullcite{OHara2009}&
		\mtri[3]{Follow the examples provided in the Books section re: varying number of authors.}
		\tabularnewline
	&Wolff and Perry (2010, p. 296) note...&
		\textcite[296]{Wolff2010} note...&
		\mtr{Wolff, H \& Perry, L 2010, `Trends in clean air legislation in Europe: particulate matter and low emission zones’, \textit{Review of Environmental Economics and Policy}, vol. 4, no. 2, pp. 293–308.}&
		\mtr{\fullcite{Wolff2010}}
		\tabularnewline
	&...marked trends (Wolff \& Perry 2010, p. 296).&
		...marked trends \parencite[296]{Wolff2010}
		\tabularnewline
Journal article --- in press&
	Smith (in press) suggests ....&
		\textcite{Smithinpress}&
		Smith, M in press, ‘Role play in education’, \textit{Creative Education}.&
		\fullcite{Smithinpress}&
		\instruction{Use ‘in press’ for articles accepted for publication, but not yet published therefore no year, volume or issue are available.}
		\tabularnewline
Journal article from supplement issue&
	Smith (2007, p. S3) explains that...&
		\textcite[S3]{Smith2007}&
		Smith, B 2007, 'The effect of caffeine on sleep', suppl. B, \textit{Journal of Sleep}, vol. 4, no. 3, pp. S3-S6.&
		\fullcite{Smith2007}&
		\instruction{Use ‘suppl.’ for journal supplement issues.}
		\tabularnewline
\midrule
Special issue with editor&
	Tudini (2004) ...&
		\textcite{Tudini2004} ...&
		Tudini, V 2004, ‘Virtual immersion: Native speaker chats as a bridge to conversational Italian’, in A Rubino (ed.), \textit{Australian Review of Applied Linguistics}, Series S, no. 18, pp. 63-80.&
		\fullcite{Tudini2004}
		\tabularnewline
\bottomrule\end{longtabu}
\subsubsection{Magazine Article}
\tbhead
Magazine article&
	Giedroyc and Reed (2012, p. 25) compare...&
		\textcite[25]{Giedroyc2010} compare...&
		Giedroyc, M \& Reed, B 2012, ‘Was Lennon really a genius?’, \textit{The Spectator}, 6 October, pp. 24–6.&
		\fullcite{Giedroyc2010}&
		\mtri[3]{Publication information will vary between magazines: some have volume and/or issue numbers, while others show the month or date of publication.}
		\tabularnewline
&
	...equivalent musicians (Giedroyc \& Reed 2012, p. 25).&
		...equivalent musicians \parencite[25]{Giedroyc2010}&
		Wolff, R 2012, ‘Warhol Warhol everywhere’, \textit{ARTnews}, vol. 111, no. 8, pp. 76–81.&
		\fullcite{Wolff2012}
		\tabularnewline
&
	...living legend (McEachen 2011, p. 82).&
		...living legend \parencite[82]{McEachen2011}.&
		McEachen, B 2011, ‘Dante on Dante’, \textit{Empire}, no. 127, pp. 82–6.&
		\fullcite{McEachen2011}
		\tabularnewline
\badrow{10}Magazine article with no author&
	\textit{The Economist} (2012, p. 86) highlights...&
		\textcite[86]{LIBOR2012}&
		\textit{The Economist} 2012, ‘Reforming LIBOR: the \$300 trillion question’, vol. 404, no. 8804, p. 86.&
		\fullcite{LIBOR2012}&
		\instruction{If a magazine article has no author, cite the magazine title as author.}
		\tabularnewline
\bottomrule\end{longtabu}
\subsubsection{Newspaper article}
\tbhead
Newspaper article&
	Westwood (2012, p. 15) states...&
		\textcite[15]{Westwood2014}&
		Westwood, M 2012, ‘Welcome into an exclusive fold’, \textit{Australian}, 4 September, p. 15.&
		\fullcite{Westwood2014}&
		\instruction{Omit initial The in English language newspaper titles, e.g. The Australian.}
		\tabularnewline
\badrow{10}\mtr{Newspaper article with no author}&
	The \textit{Australian Financial Review} (22 October 2012, p. 46) examines...&
		The \textcite{AFR2012} examines...&
		\mtr{\textit{Australian Financial Review} 2012, ‘US comes to a turning point’, 22 October, p. 46.}&
		\mtr{\fullcite{AFR2012}}&
		\mtri{If a newspaper article has no author, cite the name of the newspaper as the author and include the date of publication in brackets in-text.}
		\tabularnewline
&
	...big change (Australian Financial Review 22 October 2012, p. 46).&
		...big change \parencite{AFR2012}
		\tabularnewline
\bottomrule\end{longtabu}