\section{Sound and Visual}
\subsection{Film or television}
\tbhead{}
\mtr{Film (cinema release)}&
	&&
	Anderson, PT (dir.) 2012, The master, motion picture, Weinstein Company.&
	\fullcite{TheMaster}&
	\mtri[3]{Cite a film’s director (dir.) as main author. Where directors are not identified, cite the producer (prod.) or authoring company.}
	\tabularnewline
&
	Django Unchained (Tarantino 2012) depicts...&
		\textcite{DjangoMovie} depicts...&
		Tarantino, Q (dir.) 2012, \textit{Django unchained}, motion picture, Weinstein Company.&
		\fullcite{DjangoMovie}
		\tabularnewline
Film on DVD, Blu-Ray, videotape, iTunes etc.&
	\textit{Hugo} (Scorsese 2011) presents Méliès' as...&
		\textcite{Hugo} presents Méliès' as...&
		Scorsese, M (dir.) 2011, Hugo, DVD, Paramount.&
		\fullcite{Hugo}
		\tabularnewline
Television program&
	An episode of \textit{Dateline} (SBS 2012) examines...&
		An episode of \textcite{Dateline} examines...&
		SBS 2012, \textit{Dateline}, television program, SBS, 6 November.&
		\fullcite{Dateline}&
		\mtri[4]{
			Cite a program’s director (dir.) as main author. Where directors are not identified, cite the producer (prod.) or authoring company instead.
			For TV transmissions, include channel and screening date in your reference list entry. If year of screening differs from the year of production, include year of screening in the screening date.
		}
		\tabularnewline
\mtr{Episode of a television program/\linebreak[1]series}&
	\textit{56 Up} (Apted 2012) chronicles...&
		\citetitle{56up} \parencite{56up} chronicles...& 
		 Apted, M (dir.) 2012, \textit{56 up}, ep. 2, television program, SBS, 6 November.&
		 \fullcite{56up}
		 \tabularnewline
&
	&&
	Coulter, A (dir.) 2010, ‘Paris green’, Boardwalk empire, television program, SBS, 3 November 2012.&
	\fullcite{Coulter2010}
	\tabularnewline
Episode of a television program/\linebreak[1]series on DVD, Blu-Ray, videotape, iTunes etc.&
	In season two’s penultimate episode ‘Blackwater’ (Marshall 2012), the...&
		In season two’s penultimate episode \citetitle{GameOfThrones} \parencite{GameOfThrones}, the...&
		Marshall, N (dir.) 2012, ‘Blackwater’, \textit{Game of thrones: the complete second season}, DVD, HBO.&
		\fullcite{GameOfThrones}
		\tabularnewline
\bottomrule\end{longtabu}
\subsection{Sound and visual miscellaneous}
\tbhead{}
Music recording on CD, iTunes etc.&
	Palmer (2011) explores the theme of...&
		\textcite{Palmer2011} explores the theme of...&
		Palmer, A 2011, \textit{Amanda Palmer goes down under}, CD, Liberator Music.&
		\fullcite{Palmer2011}
		\tabularnewline
Radio programme&
	...key concerns (Adams 2012).&
		...key concerns \parencite{ImmigrantNation}.&
		Adams, P 2012, ‘Immigrant nations’, \textit{Late night live}, radio program, ABC Radio, 10 October.&
		\fullcite{ImmigrantNation}
		\tabularnewline
CD-ROM&
	...valuable tool (Oxford University Press 2010).&
		...valuable tool \parencite{OxfordLearnersDict}.&
		Oxford University Press 2010, \textit{Oxford advanced learner’s dictionary}, 8\textsuperscript{th} edn, CD-ROM, OUP, Oxford.&
		\fullcite{OxfordLearnersDict}
		\tabularnewline
Video game&
	\textit{Halo: reach} (Bungie 2010), a prequel to...&
		\textcite{HaloReach}, a prequel to...&
			Bungie 2010, Halo: reach, video game, Xbox 360, Microsoft Game Studios.&
			\fullcite{HaloReach}&
			\instruction{For most video games, cite the developing company as author.}
			\tabularnewline
\bottomrule\end{longtabu}
